Comparison of Catalogs

### 2024-07-25 compare/compare.qmd
removed compare tabset

::: panel-tabset
## Coordinates

@@

|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:------------------:|:----------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |

@@

|  LCV   |   HECATE   |                           Description                            |                  Count                  |
|:----------------:|:----------------:|:------------------:|:----------------:|
|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  | `{python} non_nan_counts["logSFR_FIR"]` |
|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_60u"]` |
|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_12u"]` |
|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_22u"]` |
|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   | `{python} non_nan_counts["logSFR_HEC"]` |
|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        | `{python} non_nan_counts["logSFR_GSW"]` |
| SFRFUV |            |             FUV derived integral star formation rate             | `{python} non_nan_counts["logSFRFUV"]`  |
| SFRHa  |            |          H{alpha} derived integral star formation rate           |  `{python} non_nan_counts["logSFRHa"]`  |

@@

```{python}
#| echo: false
mass_data.drop("logM_GSW", axis=1, inplace=True)
# Compute the correlation matrix
mass_corr_matrix = mass_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(mass_corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of Mass Values")
plt.show()

# Create a pair grid
sns.pairplot(mass_data)
plt.show()
```
:::

>>>>

## Coordinates

@@

|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:-----------------:|:----------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |

@@

|  LCV   |   HECATE   |                           Description                            |                  Count                  |
|:----------------:|:----------------:|:-----------------:|:----------------:|
|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  | `{python} non_nan_counts["logSFR_FIR"]` |
|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_60u"]` |
|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_12u"]` |
|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_22u"]` |
|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   | `{python} non_nan_counts["logSFR_HEC"]` |
|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        | `{python} non_nan_counts["logSFR_GSW"]` |
| SFRFUV |            |             FUV derived integral star formation rate             | `{python} non_nan_counts["logSFRFUV"]`  |
| SFRHa  |            |          H{alpha} derived integral star formation rate           |  `{python} non_nan_counts["logSFRHa"]`  |

@@

::: panel-tabset
## Heatmap
```{python}
mass_data.drop("logM_GSW", axis=1, inplace=True)
# Compute the correlation matrix
mass_corr_matrix = mass_data.corr()

# Create a heatmap
sns.heatmap(mass_corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of Mass Values")
plt.show()
```
## Plot Grid
```{python}
# Create a pair grid
sns.pairplot(mass_data)
plt.show()
```
:::
